\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/logotext.png} \\

### 2014-10-08 report/article_4.tex
manual placement

%\setlength{\intextsep}{0em}
\begin{wrapfigure}[17]{L}{.45\textwidth}
%\vspace{-1em}
\centering
\includegraphics[width=.43\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
%\vspace{35em}
\end{wrapfigure}

@@

Letting and sales sites may currently list some recent sales, but it's
not currently possible to see a quantitative overview of property
prices in a region, within the context of its sector, district and
postcode.

@@

\begin{wrapfigure}{r}{.4\textwidth}
\begin{center}
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
\vspace{-2em}
\end{center}
\end{wrapfigure}

>>>>

@@

Letting and sales sites may currently list some recent sales, but it's
not currently possible to see a

%\setlength{\intextsep}{0em}
\begin{wrapfigure}[16]{l}{.45\textwidth}
\vspace{.5em}
\centering
\includegraphics[width=.43\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
%\vspace{35em}
\end{wrapfigure}

\noindent quantitative overview of property
prices in a region, within the context of its sector, district and
postcode.

@@

\begin{wrapfigure}[11]{r}{.4\textwidth}
\centering
\includegraphics[width=.39\textwidth]{Figures/mockup.png}
\caption{ iOS app mock-up.}
\vspace{-2em}
\end{wrapfigure}
